### 2013-12-28 docs/seminar/evaluation.tex
writing case study
writing methods-aggregation function
starting apply methods section

***Question: Is it necessary to consider just a specific language pair? Or ML can be applied on whole the data.***

***Question: Based on discussion, there are current formulas:
\begin{center}
$SCORE_{T,q} = \{ c_{T,q}, s_{T,q}, p \}$ \\
\end{center}
\begin{center}
$SCORE_{C,q} = \{ c_{C,q}, s_{C,q}, p \}$ \\
\end{center}
\begin{center}
$SCORE_{q} = \alpha.SCORE_{T,q} + \beta.SCORE_{C,q}$ \\
\end{center}
\begin{center}
$RANK_{q} = \{ t_q, e _q, SCORE_q \}$ \\
\end{center}

How can we achieve $SCORE_{T,q}$ and $SCORE_{C,q}$?
***

***TODO: Evaluation ***

>>>>

\section{Apply The Methods and Results}
\label{sec:apply}
In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characters and data.

\subsection{Aggregation Functions}
TODO

\subsection{Learning To Rank}
TODO
